Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-09 paper/paperv3.qmd
Updating model sensitivity chunk to all be 2-tailed tests instead of 1-tailed

  list(
    h1 = summary(breed_age_mod)$coefficients,
    h2_surv = summary(pup_surv_mod)$coefficients,
    h2_recr = summary(pup_recr_mod)$coefficients,
    h3 = summary(sexrat_age_mod)$coefficients
  )
}

# Fit models with cut-off at ages 8-13
cutoff <- 8:13
mod_sens <- map(cutoff, fit_models)

# Are hypotheses supported by the model?
extract_p <- function(h, tails = 1) {
  if (tails == 1) {
    map_dbl(mod_sens, \(m) pnorm(m[[h]]["age10:age_catOld", "z value"]))
  } else if (tails == 2) {
    map_dbl(mod_sens, \(m) 2 * pnorm(m[[h]]["age10:age_catOld", "z value"],
                                     lower.tail = FALSE))
  } else {
    stop("tails must be 1 or 2")
  }
}
p_tbl <- tibble(age_cutoff = cutoff, 
                "H1 (breeding)" = extract_p("h1"),
                "H2a (survival)" = extract_p("h2_surv"),
                "H2b (recruitment)" = extract_p("h2_recr"),
                "H3 (sex ratio)" = extract_p("h3"),
                "H3 (sex ratio; 2 tail)" = extract_p("h3", tails = 2))

knitr::kable(p_tbl)

>>>>

  list(
    h1 = summary(breed_age_mod)$coefficients,
    h2_surv = summary(pup_surv_mod)$coefficients,
    h2_recr = summary(pup_recr_mod)$coefficients,
    h3 = summary(sexrat_age_mod)$coefficients,
    h1_aic = AIC(breed_age_mod),
    h2_surv_aic = AIC(pup_surv_mod),
    h2_recr_aic = AIC(pup_recr_mod),
    h3_aic = AIC(sexrat_age_mod)
  )
}

# Fit models with cut-off at ages 8-13
cutoff <- 6:14
mod_sens <- map(cutoff, fit_models)

# Are hypotheses supported by the model?
extract_p <- function(h, tails = 1) {
  if (tails == 1) {
    map_dbl(mod_sens, \(m) pnorm(m[[h]]["age10:age_catOld", "z value"]))
  } else if (tails == 2) {
    map_dbl(mod_sens, \(m) 2 * pnorm(m[[h]]["age10:age_catOld", "z value"],
                                     lower.tail = (m[[h]]["age10:age_catOld", "z value"] < 0)
                                     ))
  } else {
    stop("tails must be 1 or 2")
  }
}
extract_aic <- function(h) {
  map_dbl(mod_sens, paste(h, "aic", sep = "_"))
}
p_tbl <- tibble(age_cutoff = cutoff, 
                "H1 (breeding)" = extract_p("h1", tails = 2),
                "H2a (survival)" = extract_p("h2_surv", tails = 2),
                "H2b (recruitment)" = extract_p("h2_recr", tails = 2),
                "H3 (sex ratio; 2 tail)" = extract_p("h3", tails = 2))
aic_weight <- function(x) {
  rellik <- exp(-0.5 * (x - min(x)))
  rellik / sum(rellik)
}
aic_tbl <- tibble(age_cutoff = cutoff,
                  "H1 (breeding)" = extract_aic("h1"),
                  "H2a (survival)" = extract_aic("h2_surv"),
                  "H2b (recruitment)" = extract_aic("h2_recr"),
                  "H3 (sex ratio)" = extract_aic("h3")) %>% 
  mutate(across(-age_cutoff, aic_weight))

knitr::kable(p_tbl)
knitr::kable(aic_tbl)
